\documentclass[a4paper,11pt]{article}

% ------------------------------------------------------------
% PACKAGES
% ------------------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{margin=0.8in}

\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{xcolor}

% ------------------------------------------------------------
% STYLE SETTINGS
% ------------------------------------------------------------
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\renewcommand{\baselinestretch}{1.05}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black
}

% Section formatting
\titleformat{\section}{\large\scshape}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{5pt}

% Colors
\definecolor{achievementblue}{HTML}{1F77B4}
\definecolor{teamgreen}{HTML}{20C997}

% ------------------------------------------------------------
% DOCUMENT START
% ------------------------------------------------------------
\begin{document}

\pagestyle{empty}

% ------------------------------------------------------------
% HEADER
% ------------------------------------------------------------
\begin{center}
\textbf{\Large MD. MEHEDI HASAN} \\[3pt]
\footnotesize
\href{mailto:meetmehedi1@gmail.com}{meetmehedi1@gmail.com}\,|\,
+8801403005254\,|\,
\href{https://www.linkedin.com/in/meetmehedi}{linkedin.com/in/meetmehedi}\,|\,
\href{https://github.com/meetmehedi}{github.com/meetmehedi}
\end{center}

% ------------------------------------------------------------
% RESEARCH INTERESTS
% ------------------------------------------------------------
\section{Research Interests}
Behavioral machine learning, social engineering detection, interpretable AI, socio-economic modeling, continual learning, and geospatial risk prediction. Focused on building AI systems that are explainable, fair, and grounded in real-world human behavior.

% ------------------------------------------------------------
% EDUCATION
% ------------------------------------------------------------
\section{Education}

\textbf{Dhaka International University} \hfill \textit{Sep 2023 -- Dec 2027} \\
\textit{Bachelor of Science in Computer Science and Engineering} \\
CGPA: 3.76 / 4.00 \\

\textbf{BAF Shaheen College Jashore} \hfill \textit{Sep 2020 -- Dec 2022} \\
\textit{Higher Secondary Certificate} \\
GPA: 4.75 / 5.00

% ------------------------------------------------------------
% RESEARCH PROJECTS
% ------------------------------------------------------------
\section{Projects}

\textbf{SocialAI -- Autonomous Engagement Framework} \\
\begin{itemize}
\vspace{-1.5em}
    \item Engineered a distributed, scalable platform integrating LLM agents and resilient proxy routing for automated social media content generation and task execution at scale.
\end{itemize}

\textbf{SafeRoads -- Geospatial Risk Prediction} \\
\begin{itemize}
\vspace{-1.5em}
    \item Built a system identifying high-risk road segments using traffic, weather, and accident data.
    \item Supports urban planning and risk-aware navigation.
    \item \textit{Methods: Geospatial ML, XGBoost, Spatial Clustering}
\end{itemize}

\textbf{MeteorShield -- NASA Space Apps Challenge 2025} \\
\begin{itemize}
\vspace{-1.5em}
    \item Developed a planetary defense visualization platform using NASA NEO datasets.
    \item \textbf{Champion (Barisal Division), Global Nominee, Honorable Mention}
    \item Focused on data storytelling and public awareness.
\end{itemize}

\textbf{SaveFood -- AI for Food Waste Reduction} \\
\begin{itemize}
\vspace{-1.5em}
    \item Trained time-series ML models to predict food spoilage from IoT sensor data (F1-score: 0.89).
\end{itemize}

\textbf{AgroHub -- IoT \& ML Smart Agriculture} \\
\begin{itemize}
\vspace{-1.5em}
    \item Real-time farm monitoring and ML-driven decision support system for smallholder farmers to optimize yield.
\end{itemize}

\textbf{DevBurn — Developer Analytics Engine} \\
\begin{itemize}
\vspace{-1.5em}
    \item A robust TypeScript-based full-stack engine designed to analyze developer workflows, integrating GitHub services with burnout tracking algorithms.
\end{itemize}

\textbf{AI Learning Platform} \\
\begin{itemize}
\vspace{-1.5em}
    \item An AI-powered supplementary educational platform built to enhance university coursework with intelligent assistance and interactive tracking.
\end{itemize}

\textbf{CryptoTracker} \\
\begin{itemize}
\vspace{-1.5em}
    \item A real-time cryptocurrency portfolio management application for tracking live market data and analyzing asset performance.
\end{itemize}

% ------------------------------------------------------------
% PUBLICATIONS
% ------------------------------------------------------------
\section{Publications}

\begin{enumerate}[leftmargin=1.5em, itemsep=6pt, topsep=0pt]

\item \textbf{Hasan, M. M.}, Rakib, R., Molla, M. A., Borhan, R., Based, M. A.  
\textbf{A Socio-Economic Machine Learning Framework for Predicting Programmer Retention.}  
\textit{Accepted at BIM 2025 (Taylor and Francis Books)} \textcolor{teamgreen}{[Accepted]}

\item \textbf{Hasan, M. M.}, Mahin, A. A., Chakraborty, S., Afrose, M., Mia, M. A., Based, M. A.  
\textbf{Fraud Detection with DistilBERT A Transformer-Based Approach to Behavioral Banking Sequences.}  
\textit{Accepted at BIM 2025 (Taylor and Francis Books)} \textcolor{teamgreen}{[Accepted]}

\item \textbf{Hasan, M. M.}, Mahin, A. A., Afrose, M., Based, M. A.  
\textbf{MEWC-RL++: A Modular and Adaptive Continual Reinforcement Learning Framework for Automation Systems in Structured but Evolving Environments.}  
\textit{Accepted at ECCT 2026 (Taylor and Francis Books)} \textcolor{teamgreen}{[Accepted]}

\item Mrida, M. A. R., \textbf{Hasan, M. M.}, Ausaf, S. M. N., Ray, P. C., Based, M. A.  
\textbf{Impact of Social Media Usage on Academic Performance: A Hybrid Machine Learning and SEM Approach.}  
\textit{Accepted at ECCT 2026 (Taylor and Francis Books)} \textcolor{teamgreen}{[Accepted]}

\item Biswas, S., \textbf{Hasan, M. M.}, Rakib, R., Mahin, A. A., Afrose, M., Based, M. A.  
\textbf{Lightweight Deep Learning for Urban Traffic Intelligence: A MobileNetV2-YOLOv8 Pipeline with Adaptive Resolution Processing.}  
\textit{Accepted at ECCT 2026 (ACSR, Atlantis Press, Springer Nature)} \textcolor{teamgreen}{[Accepted]}

\item Asif, M., \textbf{Hasan, M. M.}, Based, M. A.  
\textbf{Federated and Explainable Machine Learning Framework for Cyber Attack Detection in Smart Grids.}  
\textit{Accepted at ECCT 2026 (Taylor and Francis Books)} \textcolor{teamgreen}{[Accepted]}

\item \textbf{Hasan, M. M.}, Hossain, M. A., Mahin, A. A., Khatun, F.  
\textbf{Student-YOLOv8: A YOLO-Based Deep Learning Approach for Real-Time Student Detection and Face Recognition in Classroom Attendance Monitoring Systems.}  
\textit{Accepted at EFAST 2026} \textcolor{teamgreen}{[Accepted]}

\item \textbf{Hasan, M. M.}, Pallob, M. M. I., Based, M. A.  
\textbf{Digital Transformation for Sustainable Universities: Modeling the Convergence of MIS, IoT, and Governance.}  
[Under Review (Journal)]

\item \textbf{Hasan, M. M.}, Mahin, A. A., Afrose, M., Based, M. A.  
\textbf{War, Media Bias, and Socio-Economic Consequences: A Centennial Analysis of the Narrative-Reality Index (1914--2026).}  
[Under Review (Journal)]

\item \textbf{Hasan, M. M.}, Rahman, M. M., Mrida, M. A. R., Based, M. A.  
\textbf{A Hybrid Explainable Machine Learning Framework for Customer Lifetime Value Prediction and Its Socio-Economic Implications in Emerging Digital Markets.}  
[Under Review]

\item Rakib, R., \textbf{Hasan, M. M.}, Molla, M. A., Based, M. A.  
\textbf{A Relational Database-Driven Real-Time Cryptocurrency Portfolio Management System with Automated ETL Integration.}  
[Under Review]

\item Rahman, M. M., \textbf{Hasan, M. M.}, Based, M. A.  
\textbf{SafeRoads: AI-Driven Proactive Risk Synthesis and Data-Centric Infrastructure Audits for Road Safety in Low- and Middle-Income Countries.}  
[Under Review]

\item Molla, M. A., Rakib, R., \textbf{Hasan, M. M.}, Rion, A. M., Based, M. A.  
\textbf{Machine Learning based Regression and Classification of Earthquake Magnitude using USGS Seismic Records.}  
[Under Review]

\item Molla, M. A., \textbf{Hasan, M. M.}, Rakib, R., Borhan, R., Based, M. A.  
\textbf{Urban--Rural Inequality in Tech Career Intention: A Machine Learning Perspective.}  
[Under Review]

\item \textbf{Hasan, M. M.}, Molla, M. A., Rakib, R., Borhan, R., Based, M. A.  
\textbf{Socio-Economic Determinants of Programming Skill Development in Undergraduate CS Students.}  
[Under Review]

\item Rakib, R., Molla, M. A., \textbf{Hasan, M. M.}, Borhan, R., Based, M. A.  
\textbf{Explainable AI for Understanding Motivation in Choosing Computer Science Careers.}  
[Under Review]

\item Afrose, M., \textbf{Hasan, M. M.}, Mahin, A. A., Based, M. A.  
\textbf{Fairness-Aware HIV Risk Prediction in Bangladesh Using Behavioral and Explainable AI.}  
[Under Review]

\item Mahin, A. A., \textbf{Hasan, M. M.}, Rakib, R., Molla, M. A., Based, M. A.  
\textbf{A Modular Framework for Continual Reinforcement Learning in Dynamic Robotic Environments.}  
[Under Review]

\item Mahin, A. A., \textbf{Hasan, M. M.}, Afrose, M., Mia, M. A., Based, M. A.  
\textbf{Interpretable Machine Learning for Depression Risk Classification Among Bangladeshi University Students: Identifying High-Functioning Depression.}  
[Under Review]

\item \textbf{Hasan, M. M.}, Rakib, R., Molla, M. A., Based, M. A.  
\textbf{Women’s Psychology and Its Socioeconomic Impact on Male Partners and Relationships.}  
[Ongoing Research]

\item \textbf{Hasan, M. M.}, Molla, M. A., Rakib, R., Based, M. A.  
\textbf{THE DUAL PARADOX: AI Investment and Workforce Displacement in Global Corporations.}  
[Ongoing Research]

\item Afrose, M., \textbf{Hasan, M. M.}, Based, M. A.  
\textbf{MEWC-LLM: Memory-Efficient Weight Consolidation for Large Language Models – Adaptive Stability–Plasticity Optimization for Factual Continual Learning.}  
[Ongoing Research]

\end{enumerate}

% ------------------------------------------------------------
% ACHIEVEMENTS
% ------------------------------------------------------------
\section{Achievements}

\textbf{NASA International Space Apps Challenge 2025} — Champion (Barisal), Global Nominee, Honorable Mention — \textcolor{teamgreen}{Team Polaris} \\
\textbf{National Data Analytics Competition (NDAC) 2025} — Participant\\
\textbf{Eastern Bank PLC Technovation’25 National Hackathon} 2025 — Participant \\
\textbf{BUET CSE FEST National Hackathon 2026 } -- Participant

% ------------------------------------------------------------
% PROFESSIONAL AFFILIATIONS
% ------------------------------------------------------------
\section{Professional Affiliations}

\textbf{IEEE} — Student Member (Valid through Dec 2026) \\
\textbf{IEEE Computer Society} — Student Member (Valid through Dec 2026) \\
\textbf{BASIS} -- Student Member

% ------------------------------------------------------------
% LEADERSHIP
% ------------------------------------------------------------
\section{Leadership \& Community}
\textbf{DIU Computer Programming Club} - President \hfill \textit{April 2026 -- Present} \\
\textbf{DIU CSE Speakers Club} — General Secretary \hfill \textit{May 2025 - March 2026} \\
\textbf{DIU Career Development Club} — Head, Research and Training Wing \hfill \textit{Aug 2025 -- Dec 2025} \\
\textbf{BASIS Students' Forum (DIU Chapter)} — Executive Member \hfill \textit{Sep 2024–Oct 2025}

% ------------------------------------------------------------
% TECHNICAL SKILLS
% ------------------------------------------------------------
\section{Technical Skills}

\textbf{Languages:} Python, C, Java, SQL \\
\textbf{ML Frameworks:} Scikit-learn, TensorFlow, PyTorch, Auto-sklearn, LLMs / GenAI \\
\textbf{Automation \& Bots:}  
Workflow automation, intelligent bots, web automation (Selenium, Playwright), API automation, task scheduling, RPA concepts, proxy engineering, logging \& exception handling \\
\textbf{Data Tools:} Pandas, NumPy, Matplotlib, Seaborn \\
\textbf{Dev Tools:} Git, GitHub, VS Code, Google Colab, Kaggle \\
\textbf{Specialized:} Interpretable AI (SHAP), geospatial analysis, time-series forecasting, AutoML

\vfill
\begin{center}
\footnotesize Last updated: \today
\end{center}

\end{document}
